---
title: "New_Taylor_rule_India"
author: "Kanta Ogawa"
date: "2022-11-24"
output: html_document
---

policy interest rate(overnight)
<https://fred.stlouisfed.org/series/IRSTCB01INM156N>

# inflation measure \pi_{t
-CPI_price level and CPI(inflation measure)
<https://fred.stlouisfed.org/series/CPALTT01INQ657N>

# inflation target \pi^{*}_{t} 
-2 pct, 4pct, 6pct

# Natural interest rate r^{*}_{t}
-2 pct?
<https://www.boj.or.jp/en/research/wps_rev/wps_2018/data/wp18e06.pdf>
 In the Örst approach, the natural rate is distilled as the trend component of the actual real interest rate, using the Hodrick-Prescott Ölter, a band-pass Ölter, or other more sophisticated time series methodologies.


# Resource gap measures: gap
#India potential gdp
HP filter,
It is important to note here that standalone estimates of potential output and output gap using any standard time series technique (such as a Hodrick-Prescott Filter) could yield very different results compared with LW model consistent measures, and therefore, it is not advisable to use natural rate estimated from a LW framework in a Taylor type rule that otherwise uses independently estimated measures of output gap.


<https://www.oecd.org/economy/growth/23527966.pdf>

<https://m.rbi.org.in/scripts/bs_viewcontent.aspx?Id=2239>





#Interest-rate smoothing parameter \rho
0 and 0.85


# Weight on the resource gap: \beta
0.5 and 1

`


```{r ibrary, include=FALSE}

library(tidyverse)
pacman::p_load(dplyr, mFilter, devtools,vars)
#devtools::install_github("KevinKotze/tsm")
library(tsm)

pacman::p_load(ggplot2, openxlsx,lubridate, bsts)
```



```{r read data, include=FALSE}
df_real_gdp_2015_usdollar <- read_csv("../Monetary_policy/data/india/World_Bank/Real_gdp_2015_USdollar.csv")
df_nominal_gdp <- read_csv("../Monetary_policy/data/india//World_Bank/Nominal_gdp.csv")

df_nominal_interest_india <- read_csv("../Monetary_policy/data/india/Policy_interest_rate_india_annual.csv")
df_inflation_india <- read_csv("../Monetary_policy/data/india/CPI_growth_rate_india_annual.csv")
df_price_level_india <- read_csv("../Monetary_policy/data/india/CPI_india_annual.csv")
df_real_interest <- read_csv("../Monetary_policy/data/india/World_Bank/Real_interest_rate.csv")

# from <https://ourworldindata.org/co2-emissions>
df_carbon <- read_csv("../Monetary_policy/data/Annual-co2-emissions-Our_World_in_data.csv")

```


```{r gdp, include=FALSE}
# exchange rte : 2015  64.152 rupee / per usdollar
# Price level:2010 67.293593,  2015: 100.000000,

df_real_gdp_transform <- df_real_gdp_2015_usdollar %>%
  transform(`1999` = as.numeric(1999))

df_real_gdp_transform$X1999 <-  df_real_gdp_2015_usdollar$`1999`


df_real_gdp_india_2010rupee <- df_real_gdp_transform %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "year"
  ) %>%
  mutate(year = str_remove_all(year, "X")) %>%
  mutate(year = as.integer(year)) %>%
  rename("country_code" = Country.Code, 
         "Real_GDP_2015USdollar" = value) %>%
  mutate(Real_GDP_2010rupee = Real_GDP_2015USdollar * (64.152) *(67.293593/100),
         log_Real_GDP_2010rupee = log(Real_GDP_2010rupee),
         Real_GDP_Billions_2010rupee = Real_GDP_2010rupee/(10^(9)) ) %>%
  filter(country_code == "IND") %>%
  dplyr::select(year, Real_GDP_2010rupee,log_Real_GDP_2010rupee, Real_GDP_Billions_2010rupee)



#nominal gdp
df_nominal_gdp_transform <- df_nominal_gdp%>%
  transform(`1999` = as.numeric(1999))

df_nominal_gdp_transform$X1999 <-  df_nominal_gdp$`1999`

df_nominal_gdp_india <- df_nominal_gdp_transform %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "year"
  )%>%
  mutate(year = str_remove_all(year, "X")) %>%
  mutate(year = as.integer(year)) %>%
  rename("country_code" = Country.Code, 
         "Nominal_GDP_rupee" = value) %>%
  mutate(Nominal_GDP_Billions_rupee = Nominal_GDP_rupee/(10^(9)))%>%
  filter(country_code == "IND") %>%
  dplyr::select(year, Nominal_GDP_rupee, Nominal_GDP_Billions_rupee) 

# HP filter
df_real_gdp_india_2010rupee$Real_output_gap_2010rupee_hp <- hpfilter(log(df_real_gdp_india_2010rupee$Real_GDP_2010rupee),freq=6.25, type="lambda", drift=TRUE)$cycle * 100


# bk filter <https://kevinkotze.github.io/ts-5-tut/>
df_real_gdp_india_2010rupee$Real_output_gap_2010rupee_bk <- bkfilter(log(df_real_gdp_india_2010rupee$Real_GDP_2010rupee),  pl = 6, pu = 32, drift=TRUE)$cycle * 100

# bn filter

Real_output_gap_2010rupee_bn_decomp <- bnd(log(df_real_gdp_india_2010rupee$Real_GDP_2010rupee), nlag = 8)  # apply the BN decomposition that creates dataframe

bn.trend <- ts(Real_output_gap_2010rupee_bn_decomp[, 1], start = c(1960), frequency = 1)  # first column contains trend
bn.cycle <- ts(Real_output_gap_2010rupee_bn_decomp[, 2], start = c(1960), frequency = 1)  # second column contains cycle
df_real_gdp_india_2010rupee$Real_output_gap_2016rupee_bn <- bn.cycle*100




df_combined_gdp_india <- full_join(df_real_gdp_india_2010rupee, df_nominal_gdp_india, by="year") %>%
  mutate(year = as.integer(year))

```



```{r interest and inflation rate, include=FALSE}

df_nominal_interest_india <- df_nominal_interest_india %>% 
  mutate(year=format(DATE, "%Y"),
         nominal_interest_rate_india = IRSTCB01INA156N) %>%
  dplyr::select(year, nominal_interest_rate_india)


df_inflation_india <- df_inflation_india %>%
   mutate(year=format(DATE, "%Y"),
         inflation_rate_india = CPALTT01INA659N) %>%
   dplyr::select(year, inflation_rate_india)

df_price_level_india <- df_price_level_india %>%
   mutate(year=format(DATE, "%Y"),
          price_level_india_2015 = INDCPIALLAINMEI)
  
df_price_level_india  <- df_price_level_india %>%
   mutate(price_level_india_2010 = price_level_india_2015/67.3) %>% # df_price_level_india[df_price_level_india$year == "2010", "price_level_india_2015"]) = 67.3
   dplyr::select(year, price_level_india_2010)

# real interest

  
df_real_interest_transform <- df_real_interest %>%
  transform(`1999` = as.numeric(1999))

df_real_interest_transform$X1999 <-  df_real_interest$`1999`

df_real_interest_india <- df_real_interest_transform %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "year"
  )%>%
  mutate(year = str_remove_all(year, "X")) %>%
  mutate(year = as.integer(year)) %>%
  rename("country_code" = Country.Code, 
         "Real_interest" = value) %>%
  filter(country_code == "IND") %>%
  dplyr::select(year, Real_interest)

df_real_interest_india <- df_real_interest_india[complete.cases(df_real_interest_india),]

## <https://www.jstor.org/stable/3211784#metadata_info_tab_contents>
df_real_interest_india$Natural_interest_hp <- hpfilter(df_real_interest_india$Real_interest, freq=6.25, type="lambda", drift=TRUE)$trend
# bind data
  

df_cb_india <- full_join(df_nominal_interest_india, df_inflation_india,by="year")
df_cb_india <- full_join(df_cb_india, df_price_level_india, by="year") %>%
  mutate(year = as.integer(year))
 
df_macro_india <- full_join(df_cb_india,df_combined_gdp_india, by="year")  

df_macro_india <- full_join(df_macro_india, df_real_interest_india, by="year")
 
df_macro_india <-  df_macro_india %>%
   mutate(Past_inflation_rate_1 = lag(inflation_rate_india,n=1),
          Past_inflation_rate_2 = lag(inflation_rate_india,n=2),
          Past_inflation_rate_3 = lag(inflation_rate_india,n=3),
          Past_inflation_rate_4 = lag(inflation_rate_india,n=4),
          natural_interest_2pct = 2,
          inflation_target_2pct = 2,
          inflation_target_4pct = 4,
          inflation_target_6pct = 6,
          nominal_interest_rate_india_one_yaer_lag = lag(inflation_rate_india,n=1)
          ) 
 
df_macro_india <-  df_macro_india %>%
    mutate(Expectated_inflation_rate = (Past_inflation_rate_1 + Past_inflation_rate_2 + Past_inflation_rate_3 + Past_inflation_rate_4)/4)
     

plot(x=df_macro_india$year, y=df_macro_india$nominal_interest_rate_india, 
     type='l', 
     col = 'darkorange', 
     main="Policy rate in India",
     xlab= "year",
     ylab="Policy interest rate (%)"
       )
grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")



```




```{r carbon, echo=FALSE }

# CO2 emission
df_carbon <- df_carbon %>%
  rename("year"=Year,"country_code" = Code, "CO2_t" = `Annual CO2 emissions`)%>%
  filter(year >= 1960)

df_carbon_india <- df_carbon %>%
    filter(country_code == "IND")

ggplot(data=df_carbon_india,aes(x=year,y=CO2_t)) + 
  geom_line()

```

From DICE model

# Base parametes

<https://www.pnas.org/doi/10.1073/pnas.1609244114>
2015: 31.21 2010 international US dollars / tCO2

14.598  rupee/ 2010 international US dollars

```{r carbon data creation, echo=FALSE}


# compute in US dollar base
vec_pre_2015_base <- rev(GeometricSequence(56, initial.value = (14.598*31.21)/1.03, discount.factor = 1/1.03) )

pre_2015_start_year_base <- 2015 - length(vec_pre_2015_base)
pre_2015_base <- pre_2015_start_year_base:2014



vec_post_2015_base <- GeometricSequence(8, initial.value = 14.598*31.21, discount.factor = 1.03) 
post_2015_end_year_base <- 2015 + length(vec_post_2015_base) - 1
post_2015_base <- 2015:post_2015_end_year_base



# check length
length(c(vec_pre_2015_base, vec_post_2015_base))
length(c(pre_2015_base, post_2015_base))

# combined vec
Carbon_price_2010rupee_base <- c(vec_pre_2015_base, vec_post_2015_base)
year <- c(pre_2015_base, post_2015_base)
df_carbon_price_india_base <- data.frame(year, Carbon_price_2010rupee_base) 
ggplot(data=df_carbon_price_india_base, aes(x=year, y=Carbon_price_2010rupee_base) )  +geom_line()

```

# 2.5 degree maximum - Maimum

<https://www.pnas.org/doi/10.1073/pnas.1609244114>
2015: 184.4    2010 international US dollars / tCO2

14.598  rupee/ 2010 international US dollars

```{r carbon data creation, echo=FALSE}


# compute in US dollar base
vec_pre_2015_max_max <- rev(GeometricSequence(56, initial.value = (14.598*184.4)/1.03, discount.factor = 1/1.03) )

pre_2015_start_year_max_max <- 2015 - length(vec_pre_2015_max_max)
pre_2015_max_max <- pre_2015_start_year_max_max:2014



vec_post_2015_max_max <- GeometricSequence(8, initial.value = 14.598*184.4, discount.factor = 1.03) 
post_2015_end_year_max_max <- 2015 + length(vec_post_2015_max_max) - 1
post_2015_max_max <- 2015:post_2015_end_year_max_max



# check length
length(c(vec_pre_2015_max_max, vec_post_2015_max_max))
length(c(pre_2015_max_max, post_2015_max_max))

# combined vec
Carbon_price_2010rupee_max_max <- c(vec_pre_2015_max_max, vec_post_2015_max_max)
year <- c(pre_2015_max_max, post_2015_max_max)
df_carbon_price_india_max_max <- data.frame(year, Carbon_price_2010rupee_max_max) 
ggplot(data=df_carbon_price_india_max_max, aes(x=year, y=Carbon_price_2010rupee_max_max) )  +geom_line()




```
# 2.5 degree maximum - max_100y

<https://www.pnas.org/doi/10.1073/pnas.1609244114>
2015: 106.7 2010 international US dollars / tCO2

```{r carbon data creation, echo=FALSE}



vec_pre_2015_max_100y <- rev(GeometricSequence(56, initial.value = (14.598*106.7)/1.03, discount.factor = 1/1.03) )

pre_2015_start_year_max_100y <- 2015 - length(vec_pre_2015_max_100y)
pre_2015_max_100y <- pre_2015_start_year_max_100y:2014



vec_post_2015_max_100y <- GeometricSequence(8, initial.value = 14.598*106.7, discount.factor = 1.03) 
post_2015_end_year_max_100y <- 2015 + length(vec_post_2015_max_100y) - 1
post_2015_max_100y <- 2015:post_2015_end_year_max_100y



# check length
length(c(vec_pre_2015_max_100y, vec_post_2015_max_100y))
length(c(pre_2015_max_100y, post_2015_max_100y))

# combined vec
Carbon_price_2010rupee_max_100y <- c(vec_pre_2015_max_100y, vec_post_2015_max_100y)
year <- c(pre_2015_max_100y, post_2015_max_100y)
df_carbon_price_india_max_100y <- data.frame(year, Carbon_price_2010rupee_max_100y) 
ggplot(data=df_carbon_price_india_max_100y, aes(x=year, y=Carbon_price_2010rupee_max_100y) )  +geom_line()






```





# carbon price


```{r data creation}
df_all_india <- full_join(df_macro_india,df_carbon_india, by="year")

df_all_india <- full_join(df_all_india, df_carbon_price_india_base,by="year")

df_all_india <- full_join(df_all_india,df_carbon_price_india_max_max, by="year")

df_all_india <- full_join(df_all_india,df_carbon_price_india_max_100y, by="year")


```


# base parametes

```{r base data creation}
df_all_india_base <- df_all_india %>%
  mutate(Nominal_carbon_price_base_india = price_level_india_2010*Carbon_price_2010rupee_base) %>%
  mutate(Nominal_total_carbon_cost_Billions_rupee_base = (Nominal_carbon_price_base_india * CO2_t) / 10^9) %>%
  mutate(Nominal_caron_cost_over_Nominal_GDP_pct_india_base = (Nominal_total_carbon_cost_Billions_rupee_base / Nominal_GDP_Billions_rupee) * 100) %>%
 mutate(Optimal_price_india_2010_base = (Nominal_GDP_Billions_rupee +  Nominal_total_carbon_cost_Billions_rupee_base)/ Real_GDP_Billions_2010rupee) %>% 
  mutate(Price_india_2010_from_gdp_base = Nominal_GDP_Billions_rupee / Real_GDP_Billions_2010rupee) %>%
  mutate(Real_potential_GDP_Billions_2010rupee_hp = Real_GDP_Billions_2010rupee /((Real_output_gap_2010rupee_hp/100) + 1)) %>%
  mutate(Real_potential_GDP_Billions_2010rupee_bk = Real_GDP_Billions_2010rupee /((Real_output_gap_2010rupee_bk/100) + 1))%>%
  mutate(Optimal_real_GDP_Billions_rupee_2010_hp_base = (Price_india_2010_from_gdp_base * Real_potential_GDP_Billions_2010rupee_hp) / Optimal_price_india_2010_base) %>%
  mutate(Optimal_real_GDP_Billions_rupee_2010_bk_base = (Price_india_2010_from_gdp_base * Real_potential_GDP_Billions_2010rupee_bk) / Optimal_price_india_2010_base) %>%
  mutate(Revised_output_gap_india_pct_hp_base = (( Real_GDP_Billions_2010rupee  - Optimal_real_GDP_Billions_rupee_2010_hp_base)/ Optimal_real_GDP_Billions_rupee_2010_hp_base) *100)%>%
  mutate(Revised_output_gap_india_pct_bk_base = (( Real_GDP_Billions_2010rupee  - Optimal_real_GDP_Billions_rupee_2010_bk_base)/ Optimal_real_GDP_Billions_rupee_2010_bk_base) *100)%>%
  mutate(Price_gap = ((Optimal_price_india_2010_base - Price_india_2010_from_gdp_base)/Price_india_2010_from_gdp_base)*100)

df_all_india$Real_output_gap_2010rupee_hp

df_all_india$Real_output_gap_2010rupee_bk

```




```{r data bind}


## Compare price level

g_price_level_compare_india_base  <- ggplot(data=df_all_india_base, aes(x=year, y=Optimal_price_india_2010_base, color="Optimal  price level base 2012") )  + geom_line() + ylim(0,1.2) + xlab("Quarterly Periods") + ylab("price level based 2012")

g_price_level_compare_india_base <- g_price_level_compare_india_base +geom_line(data=df_all_india_base, aes(x=year, y=Price_india_2010_from_gdp_base, color="price level base 2012") )
print(g_price_level_compare_india_base)


## Compare GDP
g_gdp_compare_india_base  <- ggplot(data=df_all_india_base, aes(x=year, y= Optimal_real_GDP_Billions_rupee_2010_base, color="(Optimal_real_GDP_Billions_rupee_2010_base") )  
+geom_line() + xlab("Quarterly Periods") + ylab("Billions of rupee  2010 base")

g_gdp_compare_india_base <- g_gdp_compare_india_base +geom_line(data=df_all_india_base, aes(x=year, y=Real_GDP_Billions_2010rupee, color="Real GDP Billions of rupee 2010 base") )
print(g_gdp_compare_india_base)

## Compare log GDP

g_log_gdp_compare_india_base  <- ggplot(data=df_all_india_base, aes(x=year, y=log(Optimal_real_GDP_Billions_rupee_2010_base), color="log Optimal real GDP Billions of rupee 2010 base") )  + geom_line()  + xlab("Quarterly Periods") 


g_log_gdp_compare_india_base <- g_log_gdp_compare_india_base+ geom_line(data=df_all_india_base, aes(x=year, y=log(Real_GDP_Billions_2010rupee), color="log Real GDP Billions of rupee 2010 base") )
print(g_log_gdp_compare_india_base)

plot(x=df_all_india_base$year, y=df_all_india_base$Revised_output_gap_india_pct_base, 
     type='l', 
     col = 'red', 
     lty=1,
     main="Revised Output gap (%) vs Conventional Real Output gap of CBO",
     xlab= "Quarterly Periods",
     ylab="Output gap (%)",
     ylim=c(-20,20)
       )

  

lines(x=df_all_india_base$year, y=df_all_india_base$Real_gdp_gap_cbo, 
      type='l',
      lty=1,
      col = 'black',
      ylim=c(-20,20),
      xlab="",
      ylab="")



legend("topright",
      legend  =c("Revised Real Output gap(%)","Conventional Real Output gap of CBO%()"),
      col=c("red", "black"),
      lwd=2,
      lty=c(1,1))

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")




```








```{r base data plot}
# "Nominal caron cost vs _Nominal_GDP (%)"
plot(x=df_all_india$year, y=df_all_india$Nominal_caron_cost_over_Nominal_GDP_pct_india, 
     type='l', 
     col = 'blue', 
     main="Nominal caron cost vs _Nominal_GDP (%)",
     xlab= "year",
     ylab="Nominal caron cost vs _Nominal_GDP (%)"
       )

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")


# price level indiia
g_price_level_compare  <- ggplot(data=df_all_india, aes(x=year, y=Optimal_price_india_base_2016, color="Optimal price level base 2016") )  + geom_line() + ylim(0,1.2) + xlab("year") + ylab("Price level based on 2016")

g_price_level_compare <- g_price_level_compare + geom_line(data=df_all_india, aes(x=year, y=price_level_india_2016, color="Price level base 2016 in India") )
print(g_price_level_compare)

# real  gdp
g_gdp_compare  <- ggplot(data=df_all_india, aes(x=year, y=Optimal_real_GDP_Billions_rupee_2016, color="Optimal real GDP Billions of rupee 2016") )  +geom_line() + xlab("year") + ylab("Billions of rupee based on 2016")

g_gdp_compare <- g_gdp_compare +geom_line(data=df_all_india, aes(x=year, y=Real_GDP_Billions_2016rupee, color="Real GDP Billions of rupee 2016") )
print(g_gdp_compare)

# lof real gdp
g_log_gdp_compare  <- ggplot(data=df_all_india, aes(x=year, y=log(Optimal_real_GDP_Billions_rupee_2016), color="log Optimal real GDP Billions of rupee 2016") )  + geom_line()  + xlab("year") 


g_log_gdp_compare <- g_log_gdp_compare +geom_line(data=df_all_india, aes(x=year, y=log(Real_GDP_Billions_2016rupee), color="log Real GDP Billions of rupee 2016") )
print(g_log_gdp_compare)

# output gap
plot(x=df_all_india$year, y=df_all_india$Revised_output_gap_india_pct, 
     type='l', 
     col = 'red', 
     lty=1,
     main="Revised Output gap (%) vs Coonventional Real Output gap esatimed by HP filter",
     xlab= "year",
     ylab="Output gap (%)",
     ylim=c(-20,20)
       )
par(new=T)
  
plot(x=df_all_india$year, y=df_all_india$Real_output_gap_2016rupee_hp, 
      type='l',
      lty=1,
      col = 'black',
      ylim=c(-20,20),
      add=TRUE,
      xlab="",
      ylab="")

par(new=T)

plot(x=df_all_india$year, y=df_all_india$Real_output_gap_2016rupee_bk, 
      type='l',
      lty=2,
      col = 'orange',
      ylim=c(-20,20),
      add=TRUE,
      xlab="",
      ylab="")

par(new=T)

plot(x=df_all_india$year, y=df_all_india$Real_output_gap_2016rupee_bn, 
      type='l',
      lty=2,
      col = 'purple',
      ylim=c(-20,20),
      add=TRUE,
      xlab="",
      ylab="")





legend("bottomright",
      legend  =c("Revised Real Output gap(%)","Real Output gap estimated by HP(%)", "Real Output gap estimated by bk(%)", "Real Output gap estimated by bn%()"),
      col=c("red", "black", "orange","purple"),
      lwd=2,
      lty=c(1,1,2,2))

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")


g_outputgap <- ggplot(data=df_all_india,aes(x=year, y=Revised_output_gap_india_pct, color=Revised_output_gap_india_pct))+geom_line() 
g_outputgap <- g_outputgap + geom_line(data=df_all_india, aes(x=year, y=Real_output_gap_2016rupee_hp, color=Real_output_gap_2016rupee_hp))
print(g_outputgap)

```





```{r Taylor rule plot}

df_all_india$Natural_interest_hp
df_all_india <- df_all_india %>%
  mutate(Revised_Policy_rule_1 = 0.85 *nominal_interest_rate_india_one_yaer_lag 
         + (1 - 0.85 )*((natural_interest_2pct + inflation_target_4pct) + 1.5* (inflation_rate_india -  inflation_target_4pct) + Revised_output_gap_india_pct), # natural interest 2%
         Revised_Policy_rule_2 = ((natural_interest_2pct + inflation_target_4pct) + 1.5* (inflation_rate_india -inflation_target_4pct) + 0.5* Revised_output_gap_india_pct), # natural interest 2%
         Revised_Policy_rule_3 = 0.85 *nominal_interest_rate_india_one_yaer_lag
         + (1 - 0.85 )*((Natural_interest_hp  + inflation_target_4pct) + 1.5* (inflation_rate_india -  inflation_target_4pct) + Revised_output_gap_india_pct), # natural interest estimated by hp
         Revised_Policy_rule_4 = ((Natural_interest_hp + inflation_target_4pct) + 1.5* (inflation_rate_india -inflation_target_4pct) + 0.5* Revised_output_gap_india_pct), # natural interest estimated by hp
         Conventional_policy_1 = 0.85 *nominal_interest_rate_india_one_yaer_lag 
         + (1 - 0.85 )*((natural_interest_2pct  + inflation_target_4pct) + 1.5* (inflation_rate_india -  inflation_target_4pct) +Real_output_gap_2016rupee_bk), # natural interest 2%
         Conventional_policy_2 = ((natural_interest_2pct  +inflation_target_4pct) + 1.5* (inflation_rate_india -  inflation_target_4pct) + Real_output_gap_2016rupee_bk), # natural interest 2%
         Conventional_policy_3 = 0.85 *nominal_interest_rate_india_one_yaer_lag 
         + (1 - 0.85 )*((Natural_interest_hp  + inflation_target_4pct) + 1.5* (inflation_rate_india -  inflation_target_4pct) +Real_output_gap_2016rupee_bk), # natural interest estimated by hp
         Conventional_policy_4 = ((Natural_interest_hp  +inflation_target_4pct) + 1.5* (inflation_rate_india -  inflation_target_4pct) + Real_output_gap_2016rupee_bk)  # natural interest estimated by hp
         ) 

  
plot(x=df_all_india$year, y=df_all_india$Revised_Policy_rule_1, 
     type='l', 
     lty=2,
     xlab= "year",
     ylab="Interest rate (%)",
     ylim=c(-5,25),
     main="Policy rule vs Actual FF rate",
     col = 'red'
       )


par(new=T)

plot(x=df_all_india$year, y=df_all_india$Conventional_policy_1, 
      type='l',
      lty=2,
      col = 'blue',
      ylim=c(-5,25),
      xlab="",
      ylab="",
      add=TRUE)

par(new=T)

df_all_india$nominal_interest_rate_india
plot(x=df_all_india$year, y=df_all_india$nominal_interest_rate_india, 
      type='l',
      lty=1,
      col = 'black',
      ylim=c(-5,25),
      xlab="",
      ylab="",
      add=TRUE)




legend("topright",
      legend  =c("Revised Policy rule 1","Conventional policy 1", "Acutual Policy rate"),
      col=c("red", "blue","black"),
      lwd=2,
      lty=c(2,2,1))

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")
```

```{r Taylor rule plot2}
  
plot(x=df_all_india$year, y=df_all_india$Revised_Policy_rule_2, 
     type='l', 
     lty=2,
     xlab= "year",
     ylab="Interest rate (%)",
     ylim=c(-10,40),
     main="Policy rule vs Actual FF rate",
     col = 'green'
       )


par(new=T)

plot(x=df_all_india$year, y=df_all_india$Conventional_policy_2, 
      type='l',
      lty=2,
      col = 'purple',
      ylim=c(-10,40),
      xlab="",
      ylab="",
      add=TRUE)

par(new=T)


plot(x=df_all_india$year, y=df_all_india$nominal_interest_rate_india, 
      type='l',
      lty=1,
      col = 'black',
      ylim=c(-10,40),
      xlab="",
      ylab="",
      add=TRUE)




legend("topright",
      legend  =c("Revised Policy rule 2","Conventional policy 2", "Acutual Federal Fund rate"),
      col=c("green", "purple","black"),
      lwd=2,
      lty=c(2,2,1))

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")
     

```


```{r Taylor rule plot3}

# baseline
# natural interest rate: estimated by hp filter
# output gap is estimated by bk

  
plot(x=df_all_india$year, y=df_all_india$Revised_Policy_rule_3, 
     type='l', 
     lty=2,
     xlab= "year",
     ylab="Interest rate (%)",
     ylim=c(-5,20),
     main="Taylor rule vs Actual Policy interest rate",
     col = 'green'
       )


par(new=T)

plot(x=df_all_india$year, y=df_all_india$Conventional_policy_3, 
      type='l',
      lty=2,
      col = 'purple',
      ylim=c(-5,20),
      xlab="",
      ylab="",
      add=TRUE)

par(new=T)


plot(x=df_all_india$year, y=df_all_india$nominal_interest_rate_india, 
      type='l',
      lty=1,
      col = 'black',
      ylim=c(-5,20),
      xlab="",
      ylab="",
      add=TRUE)




legend("topright",
      legend  =c("Revised Policy rule 3","Conventional policy 3", "Acutual Policy interest rate"),
      col=c("green", "purple","black"),
      lwd=2,
      lty=c(2,2,1))

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")
     

```

```{r Taylor rule plot4}
  
plot(x=df_all_india$year, y=df_all_india$Revised_Policy_rule_4, 
     type='l', 
     lty=2,
     xlab= "year",
     ylab="Interest rate (%)",
     ylim=c(-10,40),
     main="Policy rule vs Actual FF rate",
     col = 'green'
       )


par(new=T)

plot(x=df_all_india$year, y=df_all_india$Conventional_policy_4, 
      type='l',
      lty=2,
      col = 'purple',
      ylim=c(-10,40),
      xlab="",
      ylab="",
      add=TRUE)

par(new=T)


plot(x=df_all_india$year, y=df_all_india$nominal_interest_rate_india, 
      type='l',
      lty=1,
      col = 'black',
      ylim=c(-10,40),
      xlab="",
      ylab="",
      add=TRUE)




legend("topright",
      legend  =c("Revised Policy rule 4","Conventional policy 4", "Acutual Federal Fund rate"),
      col=c("green", "purple","black"),
      lwd=2,
      lty=c(2,2,1))

grid(nx = NULL,
     ny = NULL,
     lty = 2, col = "gray")
     

```



```{r setup, include=FALSE}

#------------------------------------------------------------------------------#
# Define variables
#------------------------------------------------------------------------------#
# Upper bound on a_3 parameter (slope of the IS curve)
a3.constraint <- -0.0025

# Lower bound on b_2 parameter (slope of the Phillips curve)
b2.constraint <- 0.025

# Set the start and end dates of the estimation sample (format is c(year,quarter))
sample.start <- c(1972) 
sample.end   <- c(2021)




# Set column names for CSV output
output.col.names <- c("Date","rstar","g","z","output gap","","All results are output from the Stage 3 model.",rep("",8),"Standard Errors","Date","y*","r*","g","","rrgap")

# Set number of iterations for Monte Carlo standard error procedure
niter <- 5000

# Because the MC standard error procedure is time consuming, we include a run switch
# Set run.se to TRUE to run the procedure
run.se <- TRUE

#------------------------------------------------------------------------------#
# United States: Read in data, run estimation, and save output
#------------------------------------------------------------------------------#
# Read in output of prepare.rstar.data.us.R


india.log.output             <-  df_macro_india$log_Real_GDP_2016USdollar
india.inflation              <-  df_macro_india$inflation_rate_india
india.inflation.expectations <- df_macro_india$Expectated_inflation_rate
india.nominal.interest.rate  <-  df_macro_india$nominal_interest_rate_india
india.real.interest.rate     <- india.nominal.interest.rate - india.inflation.expectations

# Run HLW estimation for the US
india.estimation <- run.hlw.estimation(india.log.output, india.inflation, india.real.interest.rate, india.nominal.interest.rate,
                                    a3.constraint = a3.constraint, b2.constraint = b2.constraint, run.se = run.se)

# One-sided (filtered) estimates
one.sided.est.india <- cbind(india.estimation$out.stage3$rstar.filtered,
                          india.estimation$out.stage3$trend.filtered,
                          india.estimation$out.stage3$z.filtered,
                          india.estimation$out.stage3$output.gap.filtered)




```

```{r setup, include=FALSE}
write.table(one.sided.est.india, 'output/one.sided.est.us.csv', row.names = FALSE, col.names = c("rstar","g","z","output gap"), quote = FALSE, sep = ',', na = ".")

# Save output to CSV
output.india <- format.output(india.estimation, one.sided.est.inidia, india.real.interest.rate, sample.start, sample.end, run.se = run.se)
write.table(output.us, '../Monetary_policy/data/india/natural_interest_india.csv', col.names = output.col.names, quote=FALSE, row.names=FALSE, sep = ',', na = '')

```



